\documentclass[11pt]{article}

\usepackage{changepage}
\usepackage{tikz}

\usetikzlibrary{calc,shapes.multipart,chains,arrows}

\topmargin=0.0in
\oddsidemargin=0.0in
\evensidemargin=0in
\textwidth=6.5in
\marginparwidth=0.5in
\headheight=0pt
\headsep=0pt
\textheight=9.0in

\newcommand{\sectionheader}[1]{\noindent \textbf{\large #1}}

\newenvironment{sectionbody}{\begin{adjustwidth}{6mm}{}}{\end{adjustwidth}}

\begin{document}

% Remove page numbering
\pagenumbering{gobble}

% Header
\centerline{\LARGE \bf Mark A Emmons}
\centerline{955 E Stone Creek Cir, Crystal Lake, IL 60014, USA}
\centerline{MarkAndreasEmmons@gmail.com $\cdot$ +1(815)355--8062 $\cdot$ https://Github.com/MarkEmmons}

% Line
\noindent\rule{16.5cm}{0.4pt}

% Education
\sectionheader{Education}
\begin{sectionbody}
{\bf University of Illinois at Chicago}, Chicago, Illinois \hfill Aug 2012--Dec 2015 \\
$\bullet$ Bachelor of Science in Computer Science---December 2015 \\
\indent $\cdot$ Minor in Bioengineering and a focus in Mathematics. \\
{\bf McHenry County College}, Crystal Lake, Illinois \hfill Jun 2011--Aug 2012 \\
$\bullet$ General education courses.
\end{sectionbody}

% Space
\vspace{2mm}

% Selected Coursework
\sectionheader{Selected Coursework}
\begin{sectionbody}
Linear Algebra, Abstract Algebra, Atomic and Molecular Nanotechnology, Introduction to Bioinformatics w/ Lab, Operating Systems, Artificial Intelligence, Computer Networking, Secure Operating System Design, Secure Computer Systems, Codes and Cryptography.
\end{sectionbody}

% Space
\vspace{2mm}

% Selected Projects
\sectionheader{Selected Projects}
\begin{sectionbody}
{\bf Arch Linux Installation Script} \\
%$\bullet$ A custom bash script for automating the installation process and post installation build of an Arch Linux operating system with a run time of less than ten minutes. \\
$\bullet$ Automated installation and development environment setup in Bash. \\
%$\bullet$ Full feature install in 5--10 minutes. \\
{\bf ISOMaster} \\
$\bullet$ Automated creation of Arch Linux installation ISOs utilizing Docker. \\
{\bf Notebook} \\
$\bullet$ Compile notes written in Markdown format into an easy to navigate website for easy viewing. \\
{\bf Sudoku Solver} \\
$\bullet$ Dancing Links implementation in Java for solving Sudoku puzzles using Algorithm X. \\
{\bf Credits} \\
$\bullet$ Basic cryptocurrency utilizing blockchain written in NodeJS. \\
%{\bf Intel Emulator} \\
%$\bullet$ 8080 CPU emulator written in C.
\end{sectionbody}

% Space
\vspace{2mm}

% Awards & Activities
\sectionheader{Awards \& Activities}
\begin{sectionbody}
{\bf UIC Bioengineering Student Journal} --- Editorial Board Member \\
$\bullet$ Chief Editor from Fall 2014 to Spring 2015. \\
$\bullet$ Author of {\it Advances in DNA Computing and Molecular Programming}. \\
{\bf President's Award Program Scholar} \\
%{\bf NodeSchool Chicago} --- Mentor
\end{sectionbody}

% Space
\vspace{2mm}

% Work Experience
\sectionheader{Work Experience}
\begin{sectionbody}
{\bf JP Morgan \& Chase}, Chicago, Illinois \hfill Sep 2017 -- Present \\
    \textit{Account and Reference Data Analyst} -- Contractor \\
$\bullet$ Built profiles and transmissions for Receivable Operations and provided support to ensure the delivered product met the expectations of the client. \\
$\bullet$ Communicated with project managers, connectivity analysts, and technology partners to meet client needs and deliver a finished project in a timely manner. \\
$\bullet$ Assisted the Public Sector team with tax form validation for the state of Michigan PERCENTS GO HERE. \\
$\bullet$ Assisted in maintenance of the ROSS project tracking database. \\
$\bullet$ Worked on early Enhanced Health Care projects and assisted in the creation of a comprehensive documentation for the team to use when implementing projects. \\
%$\bullet$ Set up and QC'd new customer lockboxes in a testing environment. \\
%$\bullet$ ROSSdb \\
%$\bullet$ Enhanced HC \\
%$\bullet$ Migrated lockboxes into production after receiving confirmation of successful test transmission. \\
%$\bullet$ Validated tax forms and vouchers for the state of Michigan. \\
{\bf Hahn's Bakery}, Geneva, Illinois \hfill Jun 2011 -- Jan 2017 \\
\textit{Sales Manager} \\
$\bullet$ Responsible for delivering product to off-site market locations and managing booths at said markets. \\
$\bullet$ Increased sales by 75\% while securing lasting customer relationships in the Northern Suburban markets. \\
$\bullet$ Simultaneously maintained a sanitary and orderly workstation while keeping up with an accelerated sales pace and maintaining an accurate account of inventory and profit. \\
{\bf University of Illinois at Chicago}, Chicago, Illinois \hfill Sep 2012 -- Dec 2015 \\
\textit{Student Employee} \\
$\bullet$ Balanced a 30-40 hour work week with full time engineering courses while commuting from the suburbs. \\
{\bf Freelance Web Developer} \hfill Nov 2013 -- Feb 2015
\end{sectionbody}

% Space
\vspace{2mm}

% Skills
\sectionheader{Skills}
\begin{sectionbody}
{\bf Languages} \\
$\bullet$ C/C++, Java, Bash/Zsh, Javascript (Node.js, Express, React, Redux), Python, PostgreSQL, JSON, YAML, \LaTeX, HTML5, CSS (SASS). \\
    %Ruby, 
%{\bf Operating Systems} \\
%$\bullet$ Windows (XP --- 10), Linux (Arch, Fedora, Kali, Ubuntu), OSX. \\
{\bf Tools} \\
$\bullet$ Git/Github, Docker, Webpack, Babel, Virtual Box, Postman.
    %Vim, Visual Studio, IntelliJ, 
\end{sectionbody}

\end{document}
